### 2023-09-27 accepted/COPSolver/manuscript.tex
updating paper - revisions

\begin{document}
\noindent
\textbf{COPSolver: open source software for solving combinatorial optimization and other decision problems - library for solving the multi-product batch processing time maximization problem}
\vskip0.5cm
\noindent
\textbf{Tatiana Balbi Fraga, Federal University of Pernambuco, Avenida Marielle
Franco, Bairro Nova Caruaru, Caruaru, 55014-900, PE, Brazil, tatiana.balbi@ufpe.br}\\

\noindent
\textbf{Abstract}\\
This paper presents the software COPSolver, originally developed to solve decision and/or optimization problems, especially from the combinatory optimization area. The first version of COPSolver has a application of Fraga's exact method for solving the multi-product batch processing time maximization problem. This paper address the COPSolver\_1.0-1 and the next steps that will be implemented for the software's applications development.
\vskip0.5cm

@@

Given the enormous variety of decision-making and/or optimization problems and the complexity of such problems, the scientific literature brings numerous scientific materials that deal with the various problems and propose different solution methodologies for these problems. However, it is rare to find software that solves such problems. Usually such software is closed code, developed directly to solve very specific organizational problems, and the rights of use are kept by the developers and organizations involved in the software development project. Even when this does not occur, many pieces of software developed in research projects are simply not disclosed and end up being lost over time.

@@

The first version of the software, COPSolver\_1.0-1, applies the exact solution method developed by Fraga et al. (2023) to solve the Multi-product Batch Processing Time Maximization (MBPTM) problem. This problem arises in production process operations where a set of products are processed simultaneously on the same machine, but with production rates that can be different for each product. There is a production limit for each product and also for the products group, as well as a limit for the batch processing time. The problem consists of defining the maximum processing time of the multi-product batch respecting the known restrictions. The exact method of Fraga et al. (2023) is extremely efficient, proposing solutions very quickly and with low computational cost.

@@

COPSolver is an open source software written in C++ language. Its architecture has been planned as follows: solver will be formed by a main.cpp file along with a library set (.h) and their respective source codes (.cpp). Each library will be developed to define and solve a single distinct type of problem. All libraries will contain two main structures called problem and solution, which will be used to define the parameters of the problem and the desired solution, respectively. Each library will also contain a class, called cop (for combinatorial optimization problems) or otherwise according to the nature of the problem addressed. Such class will basically contain functions for constructing/reading the problem, functions for solving the problem, and printing functions. Functions with similar purposes will be named with the same name using the functionalities of polymorphism. The libraries will be distinguished by a distinct namespace containing an acronym that identifies the problem addressed in the library itself. The definition of the problems instances can be done in three distinct ways: 1) through the data.txt file; 2) using solver predefined problems; and 3) generating a problem statically or randomly through pre-established functions of the solver. The config.txt file should be adjusted in order to: 1) inform the type of problem addressed; 2) select the method of defining the problem and the parameters that should be adjusted according to the chosen method; and 3) select the method for solving the problem. In the future, an extra library will be developed for automatic identification of the problem according to the definitions presented and for solution by the best method. For better suitability to the codeocean repository, the computational codes will be allocated within a folder named code, the files containing the input data (config.txt and data.txt) will be allocated within a folder named data, and the output files will be inserted into a folder named results. Also, files containing .h computational codes will be inserted inside a folder named lib while .cpp files (except main.cpp) will be inserted inside a folder named src. The lingo-language solvers developed for COPSolver validation will be available in specific subfolders within the folder named LINGOSolver.

@@

\section{Economic, technological, scientific and educational impact}

The determination of the maximum processing time of multi-product batches is extremely important for some industries, as it is directly related to inventory management as well as to the correct fulfillment of demand. Therefore, COPSolver\_1.0-1 can serve as an important tool for inventory control, reducing costs and improving demand compliance. As future works, we will be applying COPSolver to assist in planning the production of extruders, in companies of the plastic bag production sector. With this we hope to improve inventory management, increasing the competitive potential of these companies.

COPSolver\_1.0-1 can also be used to conduct case studies, assisting in teaching and research. Also, since COPSolver is built on the basis of problem-oriented libraries, it can also be reused in the development of other more complex software in research and technological projects.

@@

\noindent
\textbf{References}\\
Fraga, T.B., Aquino, Í.R.B. and Menêzes, R.C.S. (2023). Multi-product Batch Processing Time Maximization
Problem. Manuscript submitted for publication.  \\

>>>>

\begin{document}
\noindent
\textbf{COPSolver: open source software for solving combinatorial optimization and other decision problems - library for solving the multi-product p-batch processing time maximization problem}
\vskip0.5cm
\noindent
\textbf{Tatiana Balbi Fraga, Federal University of Pernambuco, Avenida Marielle
Franco, Bairro Nova Caruaru, Caruaru, 55014-900, PE, Brazil, tatiana.balbi@ufpe.br}\\

\noindent
\textbf{Abstract}\\
COPSolver is an open source software originally developed to solve decision and/or optimization problems, especially from the combinatory optimization area. The first version of COPSolver has a application of Fraga's exact method for solving the multi-product p-batch processing time maximization problem. Such application can have significant impacts on software development for efficiently solving p-batch problems as well as contributing to better inventory control in some industries. Also it can be applied to conduct case studies, contributing to teaching and research. This paper address the first version of COPSolver as well as some important aspects of this software and the next steps that will be implemented for it's applications development.
\vskip0.5cm

@@

Given the enormous variety of decision-making and/or optimization problems and the complexity of such problems, the literature brings numerous scientific materials that deal with the various problems and propose different solution methodologies for these problems. However, it is rare to find software that solves such problems. Usually such software is closed code, developed directly to solve very specific organizational problems, and the rights of use are kept by the developers and organizations involved in the software development project. Even when this does not occur, many pieces of software developed in research projects are simply not disclosed and end up being lost over time.

@@

The first version of the software, COPSolver\_1.0-1, applies the exact solution method developed by Fraga et al. (2023) to solve the multi-product p-batch processing time maximization (MBPTM) problem. This problem arises in production process operations where a set of products are processed simultaneously on the same machine, but with production rates that can be different for each product. There is a production limit for each product and also for the products group, as well as a limit for the batch processing time. The problem consists of defining the maximum processing time of the multi-product batch respecting the known restrictions. The exact method of Fraga et al. (2023) is extremely efficient, proposing solutions very quickly and with low computational cost.

@@

COPSolver is an open source software written in C++ language. Its architecture has been planned as follows: solver will be formed by a main.cpp file along with a library set (.h) and their respective source codes (.cpp). Each library will be developed to define and solve a single distinct type of problem. All libraries will contain two main structures called problem and solution, which will be used to define the parameters of the problem and the desired solution, respectively. Each library will also contain a class, called cop (for combinatorial optimization problems) or otherwise according to the nature of the problem addressed. Such class will basically contain functions for constructing/reading the problem, functions for solving the problem, and printing functions. Functions with similar purposes will be named with the same name using the functionalities of polymorphism. The libraries will be distinguished by a distinct namespace containing an acronym that identifies the problem addressed in the library itself. The definition of the problems instances can be done in three distinct ways: 1) through the data.txt file; 2) using solver predefined problems; and 3) generating a problem statically or randomly through pre-established functions of the solver. The config.txt file should be adjusted in order to: 1) inform the type of problem addressed; 2) select the method of defining the problem and the parameters that should be adjusted according to the chosen method; and 3) select the method for solving the problem. In the future, an extra library will be developed for automatic identification of the problem according to the definitions presented and for solution by the best method. For better suitability to the codeocean repository, the computational codes will be allocated within a folder named code, the files containing the input data (config.txt and data.txt) will be allocated within a folder named data, and the output files will be inserted into a folder named results. Also, files containing .h computational codes will be inserted inside a subfolder named lib while .cpp files (except main.cpp) will be inserted inside a subfolder named src. The lingo-language solvers developed for COPSolver validation will be available in specific subfolders within the folder named LINGOSolver.

@@

\section{Impacts}

Some industrial equipment process a set of jobs (batches) simultaneously. For production scheduling in these equipment, in addition to the sequencing and determination of the batches sizes, it is also necessary to define the set of batches that will be processed simultaneously in each time interval. These compound batches are called p-batch (parallel batching). Since most of p-batch problems are NP-Hard, many scientific works propose different local search heuristics for solving these problems (Fowler and Mönch, 2022). When applying some local search heuristics for solving a p-batch problem, it becomes necessary to determine the maximum p-batch processing time at each iteration. So, the method applied to solve this sub-problem can have a strong impact on the computational cost of the local search algorithm proposed for solving p-batch problems. As reported earlier, COPSolver's library for solving the multi-product p-batch processing time maximization problem has an application of the Fraga's method to solve this sub-problem, which has very low computational cost. Therefore, this library can be used to implement local search heuristics-based algorithms developed for solving p-batch problems, generating a high impact on the efficiency of these algorithms. An article has been submitted for publication, which present the exact method proposed for solving multi-product p-batch processing time maximization problems as well as an extensive study on the computational efficiency of the COPSolver\_1.0-1 (Fraga \emph{et al.}, 2023). In order to make this software available to the rest of the world, all the necessary files that is required to compile and run the software successfully have been published to the codeocean project (Fraga, 2023).

It is important to note that the determination of the maximum processing time of multi-product p-batches itself is extremely important for some industries, as it is directly related to inventory management as well as to the correct fulfillment of demand. Therefore, COPSolver\_1.0-1 can serve as an important tool for inventory control, reducing costs and improving demand compliance. As future works, we will be applying COPSolver to assist in planning and scheduling the production of extruders, in companies of the plastic bag production sector. With this we hope to improve inventory management, increasing the competitive potential of these companies. These works will be case studies, conducted to assist in teaching and research, so it can also generate an important impact in these aspects.

@@

\noindent
\textbf{References}\\

Fraga, T.B., Aquino, Í.R.B. and Menêzes, R.C.S. (2023). Exact method for solving the multi-product p-batch processing time maximization problem. Manuscript submitted for publication.  \\

Fraga, T.B. (2023). COPSolver: open source software for solving combinatorial optimization and other decision problems - library for solving the multi-product batch processing time maximization problem. Published Version 1.0. codeocean. Available at: https://codeocean.com/capsule/4837209/tree/v1.  \\

Fowler, J.W. and Mönch, L. (2022). A survey of scheduling with parallel batch (p-batch) processing. European Journal of Operational Research, v. 298, pp. 1–24. \\
